Real Time Adaptive Shape Reconstruction for Asteroid Landing

### 2018-08-08 manuscript.tex
Fix compile errors for dissertation additions

For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
The original unit cube is composed of \num{8} vertices and \num{12} faces.
The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
The two large triangular faces are divided into a number of smaller triangular faces.
Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.49\textwidth]{figures/computational_geometry/isotropic/original_cube.jpg}}~
    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.49\textwidth]{figures/computational_geometry/isotropic/remesh_cube.jpg}}
    \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
\end{figure}

@@

In this section, we demonstrate the use of the results presented in~\cref{sec:mathematical_background,sec:se3_control,sec:shape_reconstruction} with several numerical examples.
The incremental shape reconstruction approach from~\cref{sec:radius_update} is used to iteratively reconstruct the shape of several asteroid given \gls{lidar} measurements.
We utilize radar shape models of asteroids \num{4769} Castalia, (\num{52760}) \num{1998} \(\text{ML}_{14}\), \num{1620} Geographos, and 6489 Golevka~\cite{neese2004}.
The asteroids exhibit a wide range of shapes and demonstrate the effectiveness of the mesh update approach.
\Cref{sec:kinematic_exploration} focuses on the application of the incremental mesh update scheme of~\cref{sec:radius_update} for several different asteroids.
\Cref{sec:dynamic_exploration} incorporates the full dynamic model on \( \SE \) of a dumbbell spacecraft given in~\cref{sec:inertial_dumbbell_eoms}, the polyhedron potential model from~\cref{sec:polyhedron_potential}, and the mesh update and guidance scheme presented in~\cref{sec:radius_update}.

@@

The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction.
\Cref{tab:kinematic_asteroids} lists the true shape model parameters of asteroids Geographos and Golevka.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lccc}
        \toprule
        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
        \midrule
        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
        \bottomrule
    \end{tabular} 
    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
\end{table}
The spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
\Gls{lidar} measurements are generated until the total uncertainty
\begin{align*}
    \sum_i w_i,
\end{align*}
is sufficiently small.
In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented in~\cref{sec:polyhedron_volume}.

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/geographos/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_1872.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_3745.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_5617.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_7489.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/truth.jpg}}
    \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_1321.jpg}}\\%

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_2643.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_3964.jpg}}\\%

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_5285.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/truth.jpg}}
    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
\end{figure}

@@

In this section, we simulate a dumbbell spacecraft in motion around asteroid \num{52760} and asteroid Castalia.
The dynamic simulation utilizes the inertial equations of motion from~\cref{sec:inertial_dumbbell_eoms} and are given as
\begin{align*}
    \dot{x} &= \ivel, \\
    \parenth{m_1 + m_2} \dot{\ivel} &= - \sum_{i=0}^2 m_i R_A \deriv{U}{\apos_i} + u_f, \\
    \dot{R} &= R \iangvel, \\
    J \dot{\iangvel} + \hat{\iangvel} J \iangvel &= \sum_{i=0}^2 m_i \hat{\spos}_i R^T R_A \deriv{U}{\apos_i} + u_m. 
\end{align*}
The nonlinear controllers described in~\cref{sec:se3_control} are used to control both the translational and rotational states of the vehicle.
The control inputs are duplicated from~\cref{sec:se3_control} as
\begin{align*}
    \vc{u}_f &= -k_x e_x - k_v e_v - F_{ext} + m \ddot{x}_d . \\
    \vc{u}_m &= -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - M_{ext}.
\end{align*}
Throughout the simulation the control inputs are computed using the current shape estimate of the asteroid. 
As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states using the details provided in~\cref{sec:radius_update,sec:explore_asteroid}.
These simulations demonstrate the ability of a spacecraft to autonomously explore and maneuver around an unknown small body.

We consider two simulations about asteroids \num{52760} and Castalia.
The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
Furthermore, the state of the asteroid, namely the rotation matrix \( R_A \), is assumed to be known based on ground measurements or previous data.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lcc}
        \toprule
        Property & \num{4769} Castalia & (\num{52760}) \num{1998} \(\text{ML}_{14}\) \\
        \midrule
        Semi-major axes(\si{\kilo\meter}) & \( 0.8065 \times 0.4905 \times 0.413 \) & \( 1.1 \times 1.1 \times 1.1 \) \\
        Rotational Period (\si{\hour}) & \num{4.095} & \num{14.98} \\
        Density (\si{\gram\per\centi\meter^3}) & \num{2.1} & \num{2.1} \\
        Vertices & \num{2048}  & \num{8192} \\
        Faces & \num{4092} & \num{16320} \\
        \bottomrule
    \end{tabular}
    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
\end{table}
At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take \gls{lidar} measurements of the surface at \SI{1}{\hertz}.
Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_0}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_25}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_3749.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_50}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_7499.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_75}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_11249.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_100}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/dynamic_exploration/52760/partial_14998.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:52760_truth}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/52760/truth.jpg}}
    \caption[Asteroid 52760 incremental reconstruction]{Incremental reconstruction of asteroid 52760~\label{fig:52760_reconstruction}}
\end{figure}

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_3749.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_7499.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_11249.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/52760/partial_weights_14998.jpg}}%
    % \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.18\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/52760/truth.jpg}}
    \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760. The images colored according to the shape uncertainty. Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
\end{figure}
\Cref{fig:52760_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
The plots show that the reconstruction  converges to an accurate shape estimate after approximately \SI{8000}{\second}.

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{3D visualization of the trajectory\label{fig:52760_explore_trajectory}}{\includegraphics[trim={0 0 0 0},clip,keepaspectratio,width=0.99\textwidth]{figures/computational_geometry/dynamic_exploration/52760/state/asteroid_trajectory.jpg}
}\\%
    \subcaptionbox{Components of position\label{fig:52760_explore_components}}{\input{tikz/52760_asteroid_position.tikz}}
    \caption{Spacecraft trajectory in the rotating asteroid frame for the exploration of 52760~\label{fig:52760_trajectory}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_3749.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_7499.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_11249.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/dynamic_exploration/castalia/partial_14998.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:castalia_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/castalia/truth.jpg}}
    \caption[Asteroid Castalia incremental reconstruction]{Incremental reconstruction of asteroid Castalia~\label{fig:castalia_reconstruction}}
\end{figure}

>>>>

For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
The original unit cube is composed of \num{8} vertices and \num{12} faces.
The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
The two large triangular faces are divided into a number of smaller triangular faces.
Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.49\textwidth]{figures/original_cube.jpg}}~
    \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.49\textwidth]{figures/remesh_cube.jpg}}
    \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
\end{figure}

@@

In this section, we demonstrate the use of the results presented in~\cref{sec:mathematical_background,sec:se3_control,sec:shape_reconstruction} with several numerical examples.
The incremental shape reconstruction approach from~\cref{sec:radius_update} is used to iteratively reconstruct the shape of several asteroid given LIDAR measurements.
We utilize radar shape models of asteroids \num{4769} Castalia, (\num{52760}) \num{1998} \(\text{ML}_{14}\), \num{1620} Geographos, and 6489 Golevka~\cite{neese2004}.
The asteroids exhibit a wide range of shapes and demonstrate the effectiveness of the mesh update approach.
\Cref{sec:kinematic_exploration} focuses on the application of the incremental mesh update scheme of~\cref{sec:radius_update} for several different asteroids.
\Cref{sec:dynamic_exploration} incorporates the full dynamic model on \( \SE \) of a dumbbell spacecraft given in~\cref{sec:inertial_dumbbell_eoms}, the polyhedron potential model from~\cref{sec:polyhedron_potential}, and the mesh update and guidance scheme presented in~\cref{sec:radius_update}.

@@

The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction.
\Cref{tab:kinematic_asteroids} lists the true shape model parameters of asteroids Geographos and Golevka.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lccc}
        \toprule
        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
        \midrule
        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
        \bottomrule
    \end{tabular} 
    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
\end{table}
The spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
LIDAR measurements are generated until the total uncertainty
\begin{align*}
    \sum_i w_i,
\end{align*}
is sufficiently small.
In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented in~\cref{sec:polyhedron_volume}.

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/geographos/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_1872.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_3745.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_5617.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/partial_7489.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/mesh_update/geographos/truth.jpg}}
    \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_1321.jpg}}\\%

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_2643.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_3964.jpg}}\\%

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/partial_5285.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/golevka/truth.jpg}}
    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
\end{figure}

@@

In this section, we simulate a dumbbell spacecraft in motion around asteroid \num{52760} and asteroid Castalia.
The dynamic simulation utilizes the inertial equations of motion from~\cref{sec:inertial_dumbbell_eoms} and are given as
\begin{align*}
    \dot{x} &= v, \\
    \parenth{m_1 + m_2} \dot{v} &= - \sum_{i=0}^2 m_i R_A \deriv{U}{z_i} + u_f, \\
    \dot{R} &= R \Omega, \\
    J \dot{\Omega} + \hat{\Omega} J \Omega &= \sum_{i=0}^2 m_i \hat{\rho}_i R^T R_A \deriv{U}{z_i} + u_m. 
\end{align*}
The nonlinear controllers described in~\cref{sec:se3_control} are used to control both the translational and rotational states of the vehicle.
The control inputs are duplicated from~\cref{sec:se3_control} as
\begin{align*}
    \vc{u}_f &= -k_x e_x - k_v e_v - F_{ext} + m \ddot{x}_d . \\
    \vc{u}_m &= -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - M_{ext}.
\end{align*}
Throughout the simulation the control inputs are computed using the current shape estimate of the asteroid. 
As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states using the details provided in TODO.
These simulations demonstrate the ability of a spacecraft to autonomously explore and maneuver around an unknown small body.

We consider two simulations about asteroids \num{52760} and Castalia.
The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
Furthermore, the state of the asteroid, namely the rotation matrix \( R_A \), is assumed to be known based on ground measurements or previous data.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lcc}
        \toprule
        Property & \num{4769} Castalia & (\num{52760}) \num{1998} \(\text{ML}_{14}\) \\
        \midrule
        Semi-major axes(\si{\kilo\meter}) & \( 0.8065 \times 0.4905 \times 0.413 \) & \( 1.1 \times 1.1 \times 1.1 \) \\
        Rotational Period (\si{\hour}) & \num{4.095} & \num{14.98} \\
        Density (\si{\gram\per\centi\meter^3}) & \num{2.1} & \num{2.1} \\
        Vertices & \num{2048}  & \num{8192} \\
        Faces & \num{4092} & \num{16320} \\
        \bottomrule
    \end{tabular}
    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
\end{table}
At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take LIDAR measurements of the surface at \SI{1}{\hertz}.
Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_0}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_25}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_3749.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_50}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_7499.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_75}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_11249.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_100}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/dynamic_exploration/52760/partial_14998.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:52760_truth}}{\includegraphics[trim={10cm 0cm 10cm 0cm},clip,keepaspectratio,height=0.25\textheight]{figures/mesh_update/52760/truth.jpg}}
    \caption[Asteroid 52760 incremental reconstruction]{Incremental reconstruction of asteroid 52760~\label{fig:52760_reconstruction}}
\end{figure}

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
    % \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.18\textheight,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/52760/truth.jpg}}
    \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760. The images colored according to the shape uncertainty. Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
\end{figure}
\Cref{fig:52760_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
The plots show that the reconstruction  converges to an accurate shape estimate after approximately \SI{8000}{\second}.

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{3D visualization of the trajectory\label{fig:52760_explore_trajectory}}{\includegraphics[trim={0 0 0 0},clip,keepaspectratio,width=0.99\textwidth]{figures/dynamic_exploration/52760/state/asteroid_trajectory.jpg}
}\\%
    \subcaptionbox{Components of position\label{fig:52760_explore_components}}{\input{tikz/52760_asteroid_position.tikz}}
    \caption{Spacecraft trajectory in the rotating asteroid frame for the exploration of 52760~\label{fig:52760_trajectory}}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_3749.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_7499.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_11249.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_14998.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:castalia_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
    \caption[Asteroid Castalia incremental reconstruction]{Incremental reconstruction of asteroid Castalia~\label{fig:castalia_reconstruction}}
\end{figure}
